Exploring probability distributions for bivariate temporal granularities

### 2020-01-31 main.Rmd
caption changed - smart meter

```{r bothcust, fig.cap = "Boxplot of energy consumption across hours of the day faceted by weekday/weekend for household 1 (customer id: 10006704) and household 2 (customer id: 10017936). Median behavior for the early morning hours of household 2 is extremely high for weekends compared to weekdays, not much differenc can be observed for household 1. "}
cust1
cust2
```

```{r bothcust-lv, fig.cap ="towrite."}
# 
# smart_meter10 %>% 
#   filter(customer_id %in% c(10006704)) %>% 
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

@@

```{r cust-ridge, fig.cap ="towrite something"}
# 
# smart_meter10 %>% 
#   filter(customer_id %in% c(10006704)) %>% 
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

>>>>

```{r bothcust, fig.cap = "Quantile plots of energy consumption across hours of the day faceted by weekday/weekend for household 1 (customer id: 10006704) and household 2 (customer id: 10017936). Median behavior for the early morning hours of household 2 is extremely high for weekends compared to weekdays, not much differenc can be observed for household 1. "}
cust1
cust2
```

```{r bothcust-lv, fig.cap ="Violin plots of energy consumption across hours of the day faceted by weekday/weekend for household 2 (customer id: 10017936). Early morning hours are bimodal implying both high and low consumption are probable. Volatility is high from 7 to 13 hours as evident from the narrow violins."}
# 
# smart_meter10 %>% 
#   filter(customer_id %in% c(10006704)) %>% 
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

@@

```{r cust-ridge, fig.cap ="Boxplot of energy consumption across hours of the day faceted by weekday/weekend for household 2 (customer id: 10017936). Median behavior for the early morning hours of household 2 is extremely high for weekends compared to weekdays."}
# 
# smart_meter10 %>% 
#   filter(customer_id %in% c(10006704)) %>% 
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")
